---
title: "p8105_hw5_xw2962"
author: "Xiaoyu Wu"
date: "2023-11-04"
output: github_document
---
 
```{r}
library(dplyr)
library(tidyverse)
library(rvest)
library(purrr)
library(broom)
library(tidyr)
set.seed(1)
```

## Problem One 

#### Import Raw Data 
```{r}
homicide_df= 
  read_csv("./data/homicide-data.csv")|>
  janitor::clean_names() 
```

#### Describe the Raw Data 
The dataset homicide_df has `r ncol(homicide_df)` variables: `r colnames(homicide_df)`. And in this dataset, there are `r nrow(homicide_df)` rows. And there are `r ncol(homicide_df)` columns. Here, we consider variables: reported_date, victim_race, victim_age, victim_sex, city, state, lat, lon and disposition important for analysis. 

#### Summarize within Cities 
```{r}
city_summary=
  homicide_df |> 
  mutate(city_state = paste(city, state, sep = ", "),
# create a city_state variable
         unsolved = disposition %in% c('Closed without arrest', 'Open/No arrest')) |> 
  group_by(city) |> 
  summarise(
    total_homicides = n(),
# summarize within cities to obtain the total number of homicides
    unsolved_homicides = sum(unsolved)
  ) |> 
# summarize within cities to obtain the number of unsolved homicides
  ungroup() 
```
#### Estimate the Proportion of Homicides that are Unsolved for Baltimore 
```{r}
baltimore_df <- homicide_df  |>
  mutate(city_state = paste(city, state, sep = ", ")) |>
  filter(city_state == "Baltimore, MD")
# filter for Baltimore, MD
prop_test_result = prop.test(x = sum(baltimore_df$disposition %in% c("Closed without arrest", "Open/No arrest")),
                             n = nrow(baltimore_df),
                             correct = FALSE) 
# perform the proportion test for Baltimore
tidy_result = broom::tidy(prop_test_result)
# save the output and apply broom::tidy to get a tidy dataframe
estimated_proportion = tidy_result$estimate
conf_low = tidy_result$conf.low
conf_high = tidy_result$conf.high
# pull the estimated proportion and confidence intervals from the resulting tidy dataframe
```
#### Run prop.test for each City
```{r}
city_prop_test_results = city_summary  |> 
  mutate(
    prop_test_result = map2(unsolved_homicides, total_homicides, ~prop.test(x = .x, n = .y)),
# run prop.test for each of the cities in your dataset
    tidy_result = map(prop_test_result, broom::tidy)
  ) |>
  select(city, tidy_result) |>
  unnest(tidy_result) |>
  select(-statistic, -p.value,-parameter, -method, -alternative) 
# create a tidy dataframe with estimated proportions and CIs for each city
print(city_prop_test_results)
# print the resulted dataframe 
```
#### Create a Plot that Shows the Estimates and CIs for each City 
```{r}
ggplot(city_prop_test_results, aes(x = reorder(city, estimate), y = estimate)) +
  geom_point() +
# create a point plot that shows the estimates and CIs for each city and organize cities according to the proportion of unsolved homicides.
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
# check out geom_errorbar
  coord_flip() +  
# flips the axes to make it easier to read city names
  labs(x = "City", y = "Proportion of Unsolved Homicides",
       title = "Proportion of Unsolved Homicides with Confidence Intervals",
       subtitle = "For major cities as reported by The Washington Post") +
# add title, subtitle and axis labels
  theme_minimal()
# edit the theme 
```

